Summer 2025 ToDo

### 2025-07-23 Relations/Paper/Formalization.tex

\begin{proof}
    See \texttt{module Theorem-1-2-3} in \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. In $\mathtt{iiSeq}$, we show that these properties imply $\isWFseqm$; establishing the implication to $\gSN$ would require additional classical assumptions. The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}

>>>>

\begin{proof}
    See \texttt{module Theorem-1-2-3} in \texttt{Theorems.agda},\\
    \verb|i     : R isWN → R isUN → R isBP|\\
    $\mathtt{i^\to}$\hspace{5mm} \verb|: R isWN → R |\texttt{isUN}$^{\to}$ \verb|→ R isBP|\\
    \verb|iiSeq : R isWN → R isUN → R isRP → isWFseq- (~R R)|\\
    \verb|iii   : R isWN → R isWCR → R isRP- → dec SN → R isSN|\\
    \verb|iv    : R isCP → R isCR|
\end{proof}
\begin{proof}[Discussion.]\hfill
  \begin{description}
    \item[($i$)] In $\mathtt{i^\to}$ we again provide a slight improvement by using $\gUNto$ rather than $\gUN$.
    \item[($ii$)] This proof is inherently classical. For the closest constructive analogue to this proof we have written $\mathtt{iiSeq}$, where we replace $\gBP$ with the stronger properties $\gWN$ and $\gUN$ and we replace $\gInc$ with the weaker property $\gRP$. 
    With the original property $\gBP$ and $gRP$ we can imply the related property $gSM$ ($\gSM$ is defined in Section~\ref{sec:Hierarchy} and its relation to $gSN$ is expanded upon). The definition and further discussion of $\isWFseqm$ are provided in Section~\ref{sec:Well-foundedness}.
    \item[($iii$)] In $\mathtt{iii}$, we replace $\gInc$ with the more general property $\gRPm$. We also assume that $\gSN$ is decidable, as this allows the construction of a witness for whether an element possesses the property $\SN$, which is essential for our proof.
    \item[($iv$)] We did not formalize $\gCR \to \gCP$ as it requires cardinality assumptions. \qedhere
  \end{description}
\end{proof}
